Fast Algorithms for Intersection of Non-matching Grids Using \plucker Coordinates.

### 2016-10-07 paper_intersections.tex
Final fixes.

\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
\newcommand{\plucker}{Pl\"{u}cker }
\newcommand{\nface}{$n$-face }
\newcommand{\nfaces}{$n$-faces }
\newcommand{\ngh}{NGH }

@@

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
%\MSC[2010] 65N30 \sep %    Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods
%\MSC[2010] 35J05  %    Laplacian operator, reduced wave equation (Helmholtz equation), Poisson equation

\end{keyword}

@@

We denote $S_i$ a simplicial element with $i+1$ vertices (of dimension $i$). We call vertices, edges, faces and simplices itself the \nfaces and we denote
$M_i$ the set of all \nfaces of the simplex $S_i$.
In general, an intersection can be a point, a line segment or a polygon called \emph{intersection polygon} (IP) in common.
The intersection polygon is represented as a list of its corners called \emph{intersection corners} (IC). The IP data structure keeps also 
reference to the intersecting simplices. A data structure of a single IC consists of:
\begin{itemize}
 \item the barycentric coordinate $\vc w_K$ of IC on $K$,
 \item the dimension $d_K$ of the most specific \nface the IC lies on,
 \item the local index $i_K$ of that \nface on $K$,
\end{itemize}
for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
is called the \emph{topological position} of the IC on $K$. Moreover, as every IC is a result of a permuted
inner product of some \plucker coordinates (see Section \label{sec:1d-2d}), we store the sign of the product as well.

@@

\subsubsection{Intersections on Sides of $S_2$}
\label{sec:sides}

@@

\subsubsection{Intersections on Edges of $S_3$}
\label{sec:edges}
\begin{algorithm}  
  \caption{2d-3d intersection, ICs on edges of $S_3$}
  \label{algo:collect_23_ip_edges}

@@

The artificial composed mesh consists of a cube and two diagonal rectangular 2d meshes (see \fig{fig:fig:cube_mesh}). The bulk mesh 
A sequence of meshes was prepared with increasing number of elements ranging
form $33$ up to $2000$ thousands of elements. The mesh step for the bulk mesh was always about half the mesh step of the component mesh. 
The number of the bulk-component intersections varies from $0.1$ up to $2.0$ millions. The timing for the three compared variants
of the mesh intersection algorithm is shown on \fig{fig:cube_speed}. Every algorithm consists of the initialization phase which process all elements of the mesh 
and the intersection phase which depends only on the number of elements in the component mesh. In these terms both phases of all three variants exhibits almost 
linear time complexity. As the number of component meshes is low and they are completely inside of the bulk mesh the FS+AF variant is the fastest in particular
due to fast initialization. On the other hand the BIH variant is about two times slower than the BIH+AF variant during the intersection phase. 
That is roughly related to the average fraction of the non-intersecting 3d element in the bounding box of a 2d element.

>>>>

%\newcommand{\noteJB}[1]{{\color{Blue} \textbf{JB: } \textit{#1}}}
%\newcommand{\notePE}[1]{{\color{Orange} \textbf{PE: } \textit{#1}}}
\newcommand{\noteJB}[1]{}
\newcommand{\notePE}[1]{}

\newcommand{\plucker}{Pl\"{u}cker }
\newcommand{\nface}{$n$-face }
\newcommand{\nfaces}{$n$-faces }
\newcommand{\ngh}{NGH }

@@

%% MSC codes here, in the form: \MSC code \sep code
%% or \MSC[2008] code \sep code (2000 is the default)
\MSC[2010] 65M60 \sep %    Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods
\MSC[2010] 65D18  %    Computer graphics, image analysis, and computational geometry [See also 51N05, 68U05]

% suggestions:

% Real and complex geometry
%	51M04   	Elementary problems in Euclidean geometries
%	51M05   	Euclidean geometries (general) and generalizations

% 76S05   	Flows in porous media; filtration; seepage

% Numerical approximation and computational geometry (primarily algorithms) {For theory, see 41-XX and 68Uxx}
% 		65D18   	Computer graphics, image analysis, and computational geometry [See also 51N05, 68U05]

% Computing methodologies and applications
% 		68U01   	General
% 		68U05   	Computer graphics; computational geometry [See also 65D18]

%	Special subfields of solid mechanics
%	74L05   	Geophysical solid mechanics [See also 86-XX]
%	74L10   	Soil and rock mechanics

% Partial differential equations, initial value and time-dependent initial-boundary value problems
% 	65M50   	Mesh generation and refinement
%       65M55   	Multigrid methods; domain decomposition
%	65M60   	Finite elements, Rayleigh-Ritz and Galerkin methods, finite methods

% Partial differential equations, boundary value problems
%        65N50   	Mesh generation and refinement
%	65N55   	Multigrid methods; domain decomposition
\end{keyword}

@@

We denote $S_i$ a simplicial element with $i+1$ vertices (of dimension $i$). We call vertices, edges, faces and simplices itself the \nfaces and we denote
$M_i$ the set of all \nfaces of the simplex $S_i$.
In general, an intersection can be a point, a line segment or a polygon called \emph{intersection polygon} (IP) in common.
The intersection polygon is represented as a list of its corners called \emph{intersection corners} (IC). The IP data structure keeps also 
reference to the intersecting simplices. A data structure of a single IC consists of:
\begin{itemize}
 \item the barycentric coordinate $\vc w_K$ of IC on $K$,
 \item the dimension $d_K$ of the most specific \nface the IC lies on,
 \item the local index $i_K$ of that \nface on $K$,
\end{itemize}
for each intersecting element $K$ of the pair. The pair $\tau_K = (d_K, i_K)$
is called the \emph{topological position} of the IC on $K$. Moreover, as every IC is a result of a permuted
inner product of some \plucker coordinates (see Section \ref{sec:1d-2d}), we store the sign of the product as well.

@@

\subsubsection{Intersections on Sides of Triangle}
\label{sec:sides}

@@

\subsubsection{Intersections on Edges of Tetrahedron}
\label{sec:edges}
\begin{algorithm}  
  \caption{2d-3d intersection, ICs on edges of $S_3$}
  \label{algo:collect_23_ip_edges}

@@

The artificial composed mesh consists of a cube and two diagonal rectangular 2d meshes (see \fig{fig:cube_mesh}). The bulk mesh 
A sequence of meshes was prepared with increasing number of elements ranging
form $33$ up to $2000$ thousands of elements. The mesh step for the bulk mesh was always about half the mesh step of the component mesh. 
The number of the bulk-component intersections varies from $0.1$ up to $2.0$ millions. The timing for the three compared variants
of the mesh intersection algorithm is shown on \fig{fig:cube_speed}. Every algorithm consists of the initialization phase which process all elements of the mesh 
and the intersection phase which depends only on the number of elements in the component mesh. In these terms both phases of all three variants exhibits almost 
linear time complexity. As the number of component meshes is low and they are completely inside of the bulk mesh the FS+AF variant is the fastest in particular
due to fast initialization. On the other hand the BIH variant is about two times slower than the BIH+AF variant during the intersection phase. 
That is roughly related to the average fraction of the non-intersecting 3d element in the bounding box of a 2d element.
